Recognizing emotions with technology and starting discussions

### 2018-01-21 paper.tex
Added corrections to 'method' chapter

>>>>

\subsection{Background information}
We want to know why the users show a specific emotion at a specific moment in the shown video. In order to
do so, we're trying to find any correlation between the user's origin and the shown emotion. Therefore,
we asked them the following set of questions before each session started:
\begin{itemize}
    \item{What's your name?}
    \item{What's your gender?}
    \item{How old are you?}
    \item{Do you live alone or with others?}
    \item{Where do you live?}
    \item{Were you also raised in this city?}
    \item{Do you have any siblings?}
    \item{What's your relationship status?}
    \item{What kind of education are you currently in?}
    \item{What kind of job do you have?}
    \item{Do you have any religious convictions?}
    \item{What are your hobbies?}
    \item{Do you often go abroad?}
    \item{Do you speak any foreign languages?}
\end{itemize}

\subsection{Recording the participants}
To give a clear impression of how the sessions were conducted, see the step-by-step description below.
\begin{enumerate}
    \item{The participant and the gamemaster gather in one room, both taking place on a chair.}
    \item{The gamemaster asks the participant if they are okay with being recorded.}
    \item{The gamemaster explains how to start the movies.}
    \item{The gamemaster leaves the room.}
    \item{The participant starts the movie by clicking on a button (spacebar).}
    \item{The video (<1 minute) starts on the laptop.}
    \item{The webcam starts recording the participant while they are watching the video.}
    \item{After the video ends, the gamemaster joins the participant again.}
    \item{The gamemaster pressed a button to show the visualized model on the laptop.}
\end{enumerate}

\subsection{Conversation with the participant}
After the sessions have been conducted, we’re looking for answers. Does the visualized model show the 
correct emotions according to what the users have experienced? Does the prototype have enough incentive to start 
a discussion regarding the shown content? To get answers to these questions, we've asked our participants 
the following set of questions:
\begin{itemize}
    \item{What did you see in the video?}
    \item{How do you feel about it?}
    \item{Why do you feel that way?}
    \item{Take a look at the model. What do you think it shows?}
    \item{\emph{The gamemaster explains the model.} Does the model show how you felt about the video?}
    \item{How do you feel about the concept "Showing a video to provoke an emotional reaction?"}
    \item{What do you think about the prototype and the visualized model?}
    \item{Do you think this contributes to starting a conversation regarding people's emotions?}
    \item{Do you see yourself discussing your emotions with other people regarding the shown content?}
\end{itemize}
